---
title: "Final Project"
output: html_document
---

## load required libs
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rattle)
library(caret)
```

## Overview
Analyszing wearables data set for teh final project of this cousrse. You may find the original data set on http://groupware.les.inf.puc-rio.br/har.

## Load data set via url
```{r}
# get the data vai url
get_data <- function(url_str) {
  return(read.csv(url(url_str),header=TRUE))
}

# do for train and test set
train <- get_data("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv")
test <- get_data("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv") 
```
the data is now loaded

## Inspect the data set
```{r}
# view data size
dim(train)
dim(test)
str(train)
```


## Pre process the data
```{r}
# pre process data
clean <- function(df) {
  # remove near zero var cols / empty / NA 
  indColToRemove <- which(colSums(is.na(df) | df == "") > 0.8 * dim(df)[1]) 
  # subset
  df <- df[,-indColToRemove]
  # drop index x
  df <- df[,-1]
  return(df)
}

#do for train and test
trainClean <- clean(train)
testClean <- clean(test)
```


## Inspect the data set
```{r}
# view data size
dim(train)
dim(test)
str(train)
```
now 59 cols are left.

## Split Data
```{r}
# ttrain and train test set
train_slice_index <- createDataPartition(trainClean$classe, p=0.7, list=FALSE)
Train1 <- trainClean[train_slice_index,]
Test1 <- trainClean[-train_slice_index,]
```

## Train RF model with CV
```{r}
# set inital seed
set.seed(0)
trc <- trainControl(method="cv", number=5)
model_rf <- train(classe~., data=Train1, method="rpart", na.action = na.pass, trControl=trc)
```

## View Model
```{r}
model_rf$finalModel
```
rol_belt is the most imp factor for the split.

## Make predictions with model
```{r}
# predict
trainpred <- predict(model_rf,newdata=testClean)

# view predictions
trainpred
```

## Including Plots
```{r pressure, echo=FALSE}
# view dendrogram
fancyRpartPlot(model_rf$finalModel)
```

